% http://kjhealy.github.com/kjh-vita
%
% ------------------------------------------------------------------------
% Requirements included in a modern tex distribution:
% ------------------------------------------------------------------------
% xelatex
% fontspec.sty
% hyperrref.sty
% xunicode.sty
% color.sty
% url.sty
% fancyhdr.sty
% memoir.cls
% fontawesome.sty
%
% ------------------------------------------------------------------------
% Requirements from https://github.com/kjhealy/latex-custom-kjh:
% ------------------------------------------------------------------------
% org-preamble-xelatex.sty
% memoir-article-styles.sty
%
% ------------------------------------------------------------------------
% Optional:
% ------------------------------------------------------------------------
% git
% vc.sty
% revnum.sty
% fonts
%
% ------------------------------------------------------------------------
% Note:
%------------------------------------------------------------------------
% Because this is a hand-tweaked file, be on the look out for \medksip, 
% \bigskip and \newpage commands here and there, which are used to balance
% the layout or avoid widows & orphans, etc. You should of course add or 
% remove these as needed.
%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
\usepackage{fontawesome,url}
    
%------------------------------------------------------------------------
% Metadata
%------------------------------------------------------------------------

\def\myauthor{Kerim B. Kaylan}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Illinois at Chicago}
\def\myaddress{College of Medicine}
\def\myemail{kaylan2@uic.edu}
\def\myweb{https://www.kbkaylan.net}
\def\myphone{+1 269 861 3750}
\def\myfax{}
\def\mytwitter{}
\def\myversion{}
\def\myrevision{}

\def\myaffiliation{University of Illinois at Chicago}
\def\myauthor{Kerim B. Kaylan}
\date{}
\def\mykeywords{Kerim, Kaylan, Kerim Kaylan, Vita, CV, Resume, Engineering, Medicine}

%------------------------------------------------------------------------
% Document
%------------------------------------------------------------------------
\begin{document}

\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro}
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]{Unit-Medium}
\setmonofont[Mapping=tex-text,Scale=0.72]{PragmataPro} 

\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

\newfontface\addressblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro Medium Caption}

%------------------------------------------------------------------------
% Local commands
%------------------------------------------------------------------------

% Marginal header
% Note: as the document goes on you may need to introduce a (gradually increasing)
% \vspace element to keep the marginal header pleasingly aligned with the first 
% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}

% No bullets on labels
\renewcommand{\labelitemi}{~} 

% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%------------------------------------------------------------------------
% Address and contact block
%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize 
 \href{http://medicine.uic.edu}{College of Medicine} \\ University of Illinois at Chicago \\ \vspace{-0.05in} Chicago, \textsc{il} 60612}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.3in}
  \flushright \footnotesize  \addressblock \myphone \, \faPhone \\ 
  % {\scriptsize  \texttt{\href{http://twitter.com/kjhealy}{\mytwitter}} \, \faTwitter }  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}} \, \faGlobe}
\end{minipage}

\medskip

% Name 
\noindent{\LARGE\scheader \textsc{kerim b. kaylan}}
\reversemarginpar

\bigskip

% Education
\marginhead{\sffamily {{\vskip -0.25em} education}}

\ind M.D., College of Medicine, University of Illinois at Chicago, 2021 (expected).

\ind Ph.D., Bioengineering, University of Illinois at Urbana--Champaign, 2017.

\ind \hspace{0.35in} \footnotesize Dissertation: \emph{Dissecting combinatorial microenvironmental regulation of cell fate and function using a multi-modal arraying platform}. Advisor: Gregory H. Underhill. \normalsize\vspace{0.05in}

\ind M.S., Bioengineering, University of Illinois at Urbana--Champaign, 2016.

\ind \hspace{0.35in} \footnotesize Thesis: \emph{Engineered microenvironments for studying liver progenitor differentiation}. Advisor: Gregory H. Underhill.\normalsize\vspace{0.05in}

\ind B.S.E., Biomedical Engineeering, University of Michigan---Ann Arbor, 2012.

\ind \hspace{0.35in} \footnotesize Graduated \emph{magna cum laude}. \normalsize\vspace{0.05in}

\bigskip

% Positions
\marginhead{\sffamily {{\vskip -0.4em} positions}}

\ind Graduate Research Assistant, Tissue Development and Engineering Laboratory, Urbana, IL, 2012--2017.

\ind \hspace{0.35in} \footnotesize Principal Investigator: Gregory H. Underhill.\normalsize\vspace{0.05in}
 
\ind Co-op, Biological Technologies, Genentech, Inc., South San Francisco, CA, 2011.

\ind \hspace{0.35in} \footnotesize Manager: Guoying Jiang.\normalsize\vspace{0.05in}
 
\ind Student Engineer, NeuroNexus, Inc., Ann Arbor, MI, 2010--2011.

\ind \hspace{0.35in} \footnotesize Manager: John Seymour.\normalsize\vspace{0.05in}

\ind Undergraduate Research Assistant, Micro/Nano/Molecular Biotechnology Laboratory, Ann Arbor, MI, 2009--2011.

\ind \hspace{0.35in} \footnotesize Principal Investigator: Shuichi Takayama.\normalsize\vspace{0.05in}
 
\bigskip
 
% Publications
\marginhead{\sffamily {\vskip 0.45em} publications}

\medskip\vspace{0.20em}

\noindent\emph{Journal Articles \vspace{0.05in}}
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Roberto C. Andresen Eguiluz, Kerim B. Kaylan, Gregory H. Underhill, and Deborah E. Leckband. ``Substrate stiffness and VE-cadherin mechano-transduction coordinate to regulate endothelial monolayer integrity.'' \emph{Biomaterials}~140:~45--57. 2017.

\ind Kerim B. Kaylan, Andreas P. Kourouklis, and Gregory H. Underhill. ``High-throughput cell microarray platform for correlative analysis of cell differentiation and traction forces.'' \emph{Journal of Visualized Experiments} 121:~e55362. 2017.

\ind Kerim B. Kaylan, Stefan D. Gentile, Lauren E. Milling, Kaustubh N. Bhinge, Farhad Kosari, and Gregory H. Underhill. ``Mapping tumor cell drug responses as a function of matrix context and genotype using combinatorial cell microarrays.'' \emph{Integrative Biology} 8(12):~1221--1231. 2016.

\ind Andreas P. Kourouklis*, Kerim B. Kaylan*, and Gregory H. Underhill. ``Substrate stiffness and matrix composition coordinately control the differentiation of liver progenitor cells.'' \emph{Biomaterials} 99:~82--94. 2016.

\ind Kerim B. Kaylan*, Viktoriya Ermilova*, Ravi Chandra Yada, and Gregory H. Underhill. ``Combinatorial microenvironmental regulation of liver progenitor differentiation by Notch ligands, TGF\textbeta, and extracellular matrix.'' \emph{Scientific Reports} 6(23490). 2016.

\ind Ehsan Atefi, Darcy Fyffe, Kerim B. Kaylan, and Hossein Tavana. ``Characterization of aqueous two-phase systems from volume and density measurements.'' \emph{Journal of Chemical and Engineering Data} 61(4):~1531--1539. 2016.

\ind Hossein Tavana, Kerim Kaylan, Tommaso Bersano-Begey, Kathryn E. Luker, Gary D. Luker, and Shuichi Takayama. ``Rehydration of polymeric, aqueous, biphasic system facilitates high throughput cell exclusion patterning for cell migration studies.'' \emph{Advanced Functional Materials} 21(15):~2920--2926. 2011.

%\end{revnumerate}
%\newpage

\bigskip

\noindent\textit{Book Chapter \vspace{0.05in}}
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

\ind Kerim B. Kaylan and Gregory H. Underhill. 2016. ``Hydrogels for Hepatic Tissue Engineering,'' in \emph{Gels Handbook: Fundamentals, Properties and Applications}, vol. 2, edited by Mohammad R. Abidian, Umut A. Gurkan, Faramarz Edalat. Hackensack, \textsc{nj}: World Scientific. 427--462.

%\end{revnumerate}

\bigskip 

% Conference Presentations
\marginhead{\sffamily {\vskip -0.25em}peer-reviewed conference \newline presentations}

\noindent\textit{Oral \vspace{0.05in}}

\ind Kerim B. Kaylan, Stefan D. Gentile, Lauren E. Milling, Kaustubh N. Bhinge, Farhad Kosari, Gregory H. Underhill. ``Mapping tumor cell drug response as a function of matrix context using combinatorial cell microarrays.'' Biomedical Engineering Society Annual Meeting, Minneapolis, MN. 6 Oct 2016.

\ind Kerim B. Kaylan, Viktoriya Ermilova, Ravi Chandra Yada, Gregory H. Underhill. ``Cellular microarrays reveal combinatorial effects of Notch ligands, TGF\textbeta, and extracellular matrix on liver progenitor differentiation.'' American Society of Mechanical Engineers NanoEngineering for Medicine and Biology Conference, Houston, TX. 23 Feb 2016.

\bigskip

\noindent\textit{Poster \vspace{0.05in}}

\ind Kerim B. Kaylan, Stefan D. Gentile, Lauren E. Milling, Kaustubh N. Bhinge, Farhad Kosari, Gregory H. Underhill. ``Combinatorial cell microarrays for analyzing ECM regulation of tumor cell drug response.'' American Physician Scientists Association Annual Meeting, Chicago, IL. 25 Apr 2015.

\ind Kerim Kaylan, Viktoriya Ermilova, Gregory Underhill. ``Arrayed microenvironments for probing liver progenitor cell fate decisions.'' Biomedical Engineering Society Meeting, San Antonio, TX. 25 Oct 2014.

\pagebreak

\marginhead{\sffamily {\vskip -0.5em}local/regional conference presentations}

\noindent\emph{Oral\vspace{0.05in}}

\ind Kerim B. Kaylan. ``Combinatorial microenvironmental regulation of liver progenitor differentiation by Notch ligands, TGF\textbeta, and extracellular matrix.'' oSTEM Minority Research Symposium, Urbana, IL. 28 Apr 2016.

\ind Kerim B. Kaylan. ``Combinatorial microenvironmental regulation of liver progenitor differentiation by Notch ligands, TGF\textbeta, and extracellular matrix.'' Bioengineering Graduate Student Seminar Series, Urbana, IL. 28 Sep 2015.

\bigskip

\noindent\emph{Poster\vspace{0.05in}}

\ind Kerim B. Kaylan, Stefan D. Gentile, Lauren E. Milling, Kaustubh N. Bhinge, Farhad Kosari, Gregory H. Underhill. ``Combinatorial cell microarrays for analyzing ECM regulation of tumor cell drug response.'' Medical Scholars Program Retreat, Monticello, IL. 23 Aug 2015.

\ind Kerim B. Kaylan, Stefan D. Gentile, Lauren E. Milling, Kaustubh N. Bhinge, Farhad Kosari, Gregory H. Underhill. ``Combinatorial cell microarrays for analyzing ECM regulation of tumor cell drug response.'' College of Medicine Research Day, Urbana, IL. 16 Apr 2015.

\ind Kerim Kaylan, Viktoriya Ermilova, Gregory Underhill. ``Deconstructing combinatorial microenvironmental regulation in hepatoblastoma using cell microarrays.'' Graduate Cancer Community Fall Symposium, Urbana, IL. 16 Sep 2014.

\ind Kerim Kaylan, Viktoriya Ermilova, Gregory Underhill. ``Deconstructing combinatorial microenvironmental regulation in hepatoblastoma using cell microarrays.'' Medical Scholars Program Retreat, Monticello, IL. 23 Aug 2014.

\ind Kerim Kaylan, Viktoriya Ermilova, Gregory Underhill. ``Deconstructing combinatorial microenvironmental regulation in hepatoblastoma using cell microarrays.'' College of Medicine Research Day, Urbana, IL. 17 Apr 2014.

\ind Kerim Kaylan, Viktoriya Ermilova, Gregory Underhill. ``Deconstructing combinatorial microenvironmental regulation in hepatoblastoma using cell microarrays.'' Bioengineering Days, Urbana, IL. 21 Feb 2014.

\ind Kerim Kaylan, Ingrid Lesaca, Guoying Jiang, H\'el\`ene Gazzano-Santoro. ``Development of a functional assay for MAb1 utilizing peptide uptake.'' Genentech Analytical Development and Quality Control Poster Mixer, South San Francisco, CA. 3 Oct 2011.

\ind Kerim Kaylan, Ingrid Lesaca, Guoying Jiang, H\'el\`ene Gazzano-Santoro. ``Development of a functional assay for MAb1.'' Genentech Intern Poster Day, South San Francisco, CA. 11 Aug 2011.

\ind Kerim Kaylan, Hossein Tavana, Shuichi Takayama. ``A novel cell migration assay utilizing polymeric aqueous two-phase systems.'' Student Biomedical Research Forum, Ann Arbor, MI. 4 Nov 2010.

\pagebreak

% Grants, Honors, and Awards
\marginhead{\sffamily {\vskip -0.35em}grants, honors, and awards}

\ind Teacher Ranked as Excellent, University of Illinois at Urbana--Champaign, 2017.

\ind Teacher Ranked as Excellent, University of Illinois at Urbana--Champaign, 2016.

\ind \hspace{0.35in} \footnotesize Outstanding ratings; top 10\% of teaching assistants as ranked by their students. \normalsize\vspace{0.05in}

\ind Medical Student Interest Group Matching Grant Program, Intersociety Council for Pathology Information, \$500, 2016.

\ind I-Corps, University of Illinois at Urbana--Champaign Site Cohort 11, National Science Foundation, \$2,000, 2016.

\ind Medical Student Interest Group Matching Grant Program, Intersociety Council for Pathology Information, \$750, 2015.

\ind O'Morchoe Leadership Fellowship for Out in Medicine, University of Illinois College of Medicine, \$1,500, 2014.

\ind Summer Biomedical and Life Sciences Fellowship, University of Michigan Undergraduate Research Opportunity Program, \$4,000, 2010.

\ind Michigan Promise Scholarship, State of Michigan, \$1,000, 2008.

\ind Michigan Competitive Scholarship, State of Michigan, \$1,300, 2008.

\bigskip\bigskip

% Teaching
\marginhead{\sffamily {\vskip -0.45em}teaching}

\ind Instructor, Cell and Tissue Biology, University of Illinois College of Medicine, 2016--2017.

\ind Facilitator, WYSE summer camp, University of Illinois at Urbana--Champaign, 2016.

\ind Facilitator, Discover Bioengineering summer camp, University of Illinois at Urbana--Champaign, 2015--2016.

\ind Organizer, Bioengineering the Future, University Lab High School, Urbana, IL. 2013.

\ind Mentor, Tissue Development and Engineering Laboratory, Urbana, IL 2012--2017.

\ind \hspace{0.35in} \footnotesize Mentored 16 undergraduate students in analytical and experimental research methods. \normalsize\vspace{0.05in}

\ind Instructor, Quantitative Cell Biology, University of Michigan---Ann Arbor, 2012.

\ind Peer Mentor, Engineering Advising Center, University of Michigan---Ann Arbor, 2010--2011.

\bigskip

% Professional Service
\marginhead{\sffamily {\vskip -0.10em}professional service}

\ind Member, USMLE Preparedness Committee, University of Illinois College of Medicine, 2017--present.

\ind Member, Student Curricular Board, University of Illinois College of Medicine, 2017--present.

\ind Member, Medical Scholars Program Steering Committee, University of Illinois College of Medicine, 2017.

\ind Member, Teaching Excellence and Innovation in Education award selection committee, University of Illinois College of Medicine, 2017.

\ind Co-Chair, Medical Scholars Program Advisory Committee, University of Illinois College of Medicine, 2016--2017.

\ind Organizer, Pathology Interest Group, University of Illinois College of Medicine, 2015--2017.

\ind Co-President, Out in Medicine, University of Illinois College of Medicine, 2014--2017.

\ind Organizer, Graduate Cancer Community @ Illinois, University of Illinois at Urbana--Champaign, 2013--2016.

\ind Co-Chair, Medical Scholars Program Retreat Committee, University of Illinois College of Medicine, 2013--2014.

\ind Member, Climate Survey Steering Committee, University of Illinois at Urbana--Champaign, 2012.

\ind Member, Medical Scholars Program Retreat Committee, University of Illinois College of Medicine, 2012--2014.

\ind Member, Engineering Graduate Student Advisory Committee, University of Illinois at Urbana--Champaign, 2012--2013.

\ind Member, Medical Scholars Program Advisory Committee, University of Illinois College of Medicine, 2012--2017.

\ind Executive Board Member, Biomedical Engineering Society, University of Michigan---Ann Arbor, 2010--2011.

\bigskip

% Professional Affiliations
\marginhead{\sffamily {\vskip -0.2em}professional affiliations}

\ind American College of Physicians.

\ind Tau Beta Pi---The Engineering Honor Society.

\ind Biomedical Engineering Society.

\ind American Physician Scientists Association.

\end{document}
